---
title: "UCI HAR Datakey"
author: "John Goodwin"
date: "March 19, 2018"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
library(tidyverse)
```

### Summary:

This is a datakey for an abbreviated dataset from the University of California-Irvine's Human Activity Recognition database. [More information on the UCI HAR database and specific fields can be found here.](http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones) Downloading the data folder from this website will give you access to "features_info.txt" which contains more information on specific variables and how they were derived. This data key is intended as a summary of this file. This key can be read in two parts. The first part contains a key for interpretting elements of the field names and the second part contains the raw field names in the dataset.

## Elements table 

```{r}
Element<- c("time",
      "freq",
      "Body",
      "Gravity",
      "Acc",
      "Gyro",
      "StdDev",
      "Mean",
      "Mag",
      "Jerk",
      "XYZ")

Description <- c("time domain signals captured at rate of 50 Hz",
                 "frequency domain signals",
                 "body acceleration signal",
                 "gravity acceleration signal",
                 "measurement from accelerometer",
                 "measurement from gyroscope",
                 "standard deviation value",
                 "mean value",
                 "magnitude of three dimensional signals",
                 "jerk signals",
                 "direction X, Y, or Z")
df <- data.frame(Element, Description)

knitr::kable(df)
```

## Variable Names

```{r}
uci_data <- read_csv("./uci_har.csv", n_max = 100 )
knitr::kable(x = colnames(uci_data), col.names = "UCI HAR Variables")
```

